---
title: "R Notebook"
output: html_notebook
---


read the file, senate dataset combined with stock info like sector, price share etc
```{r}
df = read.table('C:/Users/nour/updated_senate_data_with_stock_info.csv',sep=',',header = TRUE)
head(df)
```
```{r}
library(dplyr)
library(tidyr)
```



```{r}
senate_stocks = read.csv('C:/Users/nour/Downloads/asset_allocation_senate_stocks.csv')#('C:/Users/nour/stock_returns.csv')#('C:/Users/nour/senate_sigma.csv')
senate_stocks = as.matrix(senate_stocks)
mu = colMeans(senate_stocks)
sigma = cov(senate_stocks)
#sigma = cov(sigma)
#diag(sigma) <- runif(m)
solve(sigma)
```


#TODO: need to find stock over time to calculate sigma!! 
##https://www.kaggle.com/datasets/paultimothymooney/stock-market-data
finding the weights of the assets senators have purchased -- j
#TODO: join with senate dataset
#TODO: find covariances!!!
#TODO: find Sharpe ratio
#TODO: pick weights
```{r}
library(quadprog) # library for solve.QP
m = 1000 #length(mu) #50 #219  # no. of points to evaluate
muP = seq(0,.001,length=m) 

#sigma1 = sigma[1:50,1:50]#diag(m)#sigma[1:50,1:50]#diag(m) #sigma[1:50,1:50]
sdP = rep(0, length(muP)) # sd of portfolio return
weight = matrix(0,nrow=m,ncol=10) # storage for portfolio weights


for (i in 1:length(muP)) { # find the optimal portfolios
  result = solve.QP(Dmat=2*sigma,dvec=rep(0,10),  #3
  Amat = cbind(rep(1,10),mu),bvec=c(1,muP[i]),meq=2)
  sdP[i] = sqrt(result$value)
  weight[i,] = result$solution
}

GMP = which.min(sdP) # global minimum point
# efficient frontier
plot(sdP[GMP:m],muP[GMP:m])
points(sdP[1:(GMP-1)],muP[1:(GMP-1)], type="l", lty = 2,lwd=3, col = "red")
points(sqrt(diag(sigma)), mu, pch = 4) 
text(sqrt(diag(sigma))+0.00035, mu, colnames(senate_stocks))
```


```{r}
colnames(senate_stocks)
```

```{r}

GMP = which.min(sdP) # global minimum point
# efficient frontier
plot(sdP[GMP:m],muP[GMP:m])
plot(sdP[1:(GMP-1)],muP[1:(GMP-1)], type="l",lty = 2,lwd=3, col = "red")
plot(sqrt(diag(sigma)), mu, pch = 4,xlim = c(0.012,0.02)) 
text(sqrt(diag(sigma))+0.00035, mu, colnames(senate_stocks))
```


below is the sharpe ratio, earnings and weights of the efficient frontier of market
```{r}
sdP[GMP]
muP[GMP]
muP[GMP] / sdP[GMP]
weight[GMP,]
```


```{r}
market_stocks = read.csv('C:/Users/nour/Downloads/asset_allocation_market_stocks.csv')
market_stocks = as.matrix(market_stocks)
mu = colMeans(market_stocks)
sigma = cov(market_stocks)

solve(sigma)
```

```{r}
library(quadprog) # library for solve.QP
m = 1000 #length(mu) #50 #219  # no. of points to evaluate
muP = seq(.001,.004,length=m) 

#sigma1 = sigma[1:50,1:50]#diag(m)#sigma[1:50,1:50]#diag(m) #sigma[1:50,1:50]
sdP = rep(0, length(muP)) # sd of portfolio return
weight = matrix(0,nrow=m,ncol=10) # storage for portfolio weights


for (i in 1:length(muP)) { # find the optimal portfolios
  result = solve.QP(Dmat=2*sigma,dvec=rep(0,10),  #3
  Amat = cbind(rep(1,10),mu),bvec=c(1,muP[i]),meq=2)
  sdP[i] = sqrt(result$value)
  weight[i,] = result$solution
}

GMP = which.min(sdP) # global minimum point
# efficient frontier
plot(sdP[GMP:m],muP[GMP:m])
points(sdP[1:(GMP-1)],muP[1:(GMP-1)], type="l",
lty = 2,lwd=3, col = "red")
points(sqrt(diag(sigma)), mu, pch = 4) 
text(sqrt(diag(sigma))+0.00035, mu, colnames(market_stocks))
```




```{r}
GMP = which.min(sdP) # global minimum point
# efficient frontier
plot(sdP[GMP:m],muP[GMP:m])
plot(sdP[1:(GMP-1)],muP[1:(GMP-1)], type="l",
lty = 2,lwd=3, col = "red")
plot(sqrt(diag(sigma)), mu, pch = 4) 
text(sqrt(diag(sigma))+0.1, mu, colnames(market_stocks))
```

below is the sharpe ratio, earnings and weights of the efficient frontier of market
```{r}
GMP
sdP[GMP]
muP[GMP]
muP[GMP] / sdP[GMP]
weight[GMP,]
```


